Tool-driven Revolutions in Archaeological Science

### 2018-11-16 analysis/paper/jcaa-paper.Rmd
gave reason why ecology is a good comparison for archaeology and added citation.

The question of predicting or generating change in scientific practice via adoption of new tools is especially intruiging, and in this section we explore how a change that has been observed in ecology might be relevant for understanding or even directing the future of archaeology.

>>>>

The question of predicting or generating change in scientific practice via adoption of new tools is especially intruiging, and in this section we explore how a change that has been observed in ecology might be relevant for understanding or even directing the future of archaeology. Biological disciplines have a long tradition of influencing archaeological thought, starting with Oscar Montelius, whose typological method was inspired by Darwin's theory of evolution [@Montelius_1899, 237]. Also nowadays quite a number of spatial statistical algorithms used in archaeology are derived from Ecology [@keron_use_2015, 7].
